Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-06-04 paper.tex
Drop Neutrinosurface Approximation section

\subsection{Neutrinosurface Approximation}
\label{ssec:neutrinosurface}
\todo{derive $\tau=2/3$ approx \cite[Chap.~4]{shu1991-book_radiation},
  and \cite{miln1921-radiative_equil_1}}
In the simplified configuration of a plane-parallel atmosphere, the
rendering equation reduces to 
\begin{equation}
\label{eqn:neutrinosurface}
  f(\lambda) = f^{\rm eq}(\lambda_e),
\end{equation}
where $\tau(\lambda,\lambda_e)=2/3$.
At an optical depth of $2/3$, the energy flux is equivalent to the
blackbody value $\sigma T^4$, with $\sigma$, the Stefan-Boltzmann radiation
constant.
\todo{verify}

@@

\subsection{Gravitational Redshift and Geodesic Curvature}
\label{ssec:test_gravity}
Optically thick star in Schwarszchild.
todo{describe $L(r)$, as a function of lapse}
optically thick disk in Kerr (Fishbone-Moncrief disk):
set up to give two different surfaces for nue vs nua, but same temp (?).
\todo{plot of analytic and numerical geodesics}
\todo{plot of $G$ nue vs nua}

>>>>

@@

\subsection{Gravitational Redshift and Geodesic Curvature}
\label{ssec:test_gravity}
Optically thick star in Schwarszchild.
\todo{describe $L(r)$, as a function of lapse}
optically thick disk in Kerr (Fishbone-Moncrief disk):
set up to give two different surfaces for nue vs nua, but same temp (?).
\todo{plot of analytic and numerical geodesics}
\todo{plot of $G$ nue vs nua}
